to change

### 2023-04-09 script/report.Rmd
add report; repove 06_report/

---
title: "MSGenova Rmakrdown Report"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: no
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: no
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  result_dir: result_dir
  rmd: "report.Rmd"
  AR: AR
---

```{r setup, include=FALSE}
workspace<-params$result_dir
knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=FALSE, message=FALSE)
```

```{r load_library, echo=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
library(yaml)

config_advanced_file<-paste0(workspace,"/00_logs/config_advanced")
config_ad<-read_yaml(config_advanced_file)
```
# Tools used

```{r tools_used}
space=paste0(workspace,"/00_logs/envs")
for (file in list.files(space)){
  env<-read_yaml(paste0(space,"/",file))
  for (envi in env$dependencies){
    line=sub("=="," version ",envi)
    cat(line,"\n")
  }
}
```

# Trimming
trimmomatic PE `r config_ad$params_trimmomatic ` input_r1 input_r2 output_r1 output_r2 TRAILING:3 2> log

# Alignments

## alignments
bwa mem -R "@RG\tID:sample\tSM:sample\tLB:Illumina\tPL:Illumina\tPU:sample" -M `r config_ad$params_bwa` reference input_fq1 input_fq2 > output

## convert sam to bam
picard SortSam --INPUT input --OUTPUT output --SORT_ORDER coordinate `r config_ad$params_sort_sam`

## mark duplicates
picard MarkDuplicates --INPUT input --OUTPUT{output -M metrics `r config_ad$params_mark_duplicate`

# QC bam

## flagstat
samtools flagstat `r config_ad$params_flagstat ` input > output

## samtools coverage
samtools coverage -o output `r config_ad$params_samtools_coverage ` input

## samtools depth
samtools depth `r config_ad$params_samtools_depth`  input > output

# SV Calling

## Run haplotyCallze
gatk HaplotypeCaller -R reference -I input -O output -L region --native-pair-hmm-threads 16 `r config_ad$params_haplotype_caller`

## Run GenomicsDB
gatk GenomicsDBImport variant --genomicsdb-workspace-path output --intervals {params.region} `r config_ad$params_genomics_db`

## Run GenotypeGVCF
gatk GenotypeGVCFs --reference reference -V gendb://input -O output `r config_ad$params_genotype_gvcf`

## Merge gvcf
picard GatherVcfs list_of_vcf_files O=output `r config_ad$params_gathervcf`

## Build snpeff database
snpEff build -c output `r config_ad$params_snpeff_build` -gff3 -v reference -dataDir .

## Annotate variant
snpEff eff -c input `r config_ad$params_snpeff_ann` -dataDir . reference -s output.html input > output

# Run pindel
## run pindel
pindel `r config_ad$params_run_pindel`  -f reference -i input -o output

## convert pindel to vcf
pindel2vcf `r config_ad$params_convert_pindel` -r reference -P sample name -R xxx -d xx -v output

## Index vcf files and merge them
tabix input
bcftools merge -m none -Oz `r config_ad$params_merge_vcf_files` -o output list_vcf_files

# Run tdnascan for vaector check

## Cut multi-fasta vector file in individual files
faSplit byname input output_directory `r config_ad$params_cut_vector`

## run tdnascan
python2.7 tdnascan.py -1 input_fq1 -2 input_fq2 -t vector_sequence -g reference -p vector_name -i script_directory -d output_directory `r config_ad$params_tdnascan`

## run tdnascan annotate
python2.7 tdnascan_annotate.py -i input -f annotation_file -o output `r config_ad$params_tdnascan_annotate`

>>>>

---
title: "to change"
author: " "
date: "2022-08-16"
output:
    html_document:
        highlight: tango
        number_sections: no
        theme: default
        toc: yes
        toc_depth: 3
        toc_float:
            collapsed: no
            smooth_scroll: yes
params:
  DP.min: DP.min
  AR.min: AR.min
  result_dir: result_dir
  rmd: "report.Rmd"
  AR: AR
---

```{r setup, include=FALSE}
# title: "`r params$title`"
knitr::opts_chunk$set(root.dir=workspace, echo = FALSE , warning=FALSE, error=TRUE, message=FALSE)
```

```{r }
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
library(yaml)

```

```{r}
workspace<-params$result_dir
```

## Trimming parameters

```{r trimmomatic}
trimmo<-paste0(workspace,"/01_sequence_qc/log/trimmomatic.log")
dat<-read.table(text=gsub(" ","\t",readLines(trimmo)),  header=TRUE)
DT::datatable(dat)
```

## Mapping parameters

### Flagstat results

```{r flagstat}
library(tidyverse)
file <- paste0(workspace,"/02_mapping/flagstat/concatenate_flagstat.txt")
if(file.exists(file)){
    flagstat <- read.table(file, sep="\t", header=FALSE) %>% 
      dplyr::mutate(mapped=V3-V4, unmapped=V2-V3, supplementary=V4, 
                    mapped.ratio=round(mapped/(mapped+unmapped)*100,2), 
                    unmapped.ratio=round(unmapped/(mapped+unmapped)*100,2),
                    supplementary.ratio=round(supplementary/(mapped+unmapped)*100,2)) %>% dplyr::select(-V2, -V3, -V4)
    names(flagstat) <- c("sample", "mapped", "unmapped", "supplementary", "mapped.ratio", "unmapped.ratio", "supplementary.ratio")

  }

DT::datatable(flagstat, options = list(rownames = TRUE, pageLength = 10, scrollX = T, dom = 'tip'),class = 'cell-border stripe')
#count
nbr.reads.melt <- flagstat %>% dplyr::select(sample, mapped, unmapped, supplementary) %>% reshape2::melt(id = "sample", value.name = "nbr.reads")
summary.nbr <- nbr.reads.melt %>% group_by(variable) %>% summarise(median=median(nbr.reads), max=max(nbr.reads), min=min(nbr.reads))
nbr.reads.melt <- left_join(nbr.reads.melt, summary.nbr, by = "variable") %>% mutate(x.label=paste0(variable, "\nmedian=", median, "\nmax=", max, "\nmin=", min))
ggplot(data = nbr.reads.melt, aes(y=nbr.reads, x=x.label)) + geom_boxplot()  + xlab("") + ylab("number of reads") + ggtitle("Boxplot representing the number of mapped/supplementary/unmapped reads")+theme_bw()
#ratio
ratio.reads.melt <- flagstat %>% dplyr::select(sample, mapped.ratio, supplementary.ratio) 
names(ratio.reads.melt) <- c("sample", "mapped", "supplementary")
ratio.reads.melt <- ratio.reads.melt %>% reshape2::melt(id = "sample", value.name = "ratio")
summary.ratio <- ratio.reads.melt %>% group_by(variable) %>% summarise( median=round(median(ratio),2), max=round(max(ratio),2), min=round(min(ratio),2))
ratio.reads.melt <- left_join(ratio.reads.melt, summary.ratio, by = "variable") %>% mutate(x.label=paste0(variable, "\nmedian=", median, "%\nmax=", max, "%\nmin=", min, "%"))
ggplot(data = ratio.reads.melt) + geom_boxplot(aes(y=ratio, x=x.label)) + xlab("") + ylab("% reads") + scale_y_continuous(breaks = seq(0, max(ratio.reads.melt$ratio)+10, 20)) + ggtitle("Boxplot representing the percentage of mapped reads and supplementary alignments")+theme_bw()

```

```{r SNV_InDels_calling.Rmd}

  out <- NULL

  out <- c(out, knitr::knit_child("SNV_InDels_calling.Rmd"), quiet=TRUE)

knitr::asis_output(out)

```

```{r SV_calling.Rmd}

  out <- NULL

  out <- c(out, knitr::knit_child("SV_calling.Rmd"), quiet=TRUE)

knitr::asis_output(out)

```

```{r tDNA_scan.Rmd}

  out <- NULL

  out <- c(out, knitr::knit_child("tDNA_scan.Rmd"), quiet=TRUE)

knitr::asis_output(out)

```

# Tools used

```{r tools}

  out <- NULL

  out <- c(out, knitr::knit_child("tools.Rmd"), quiet=TRUE)

knitr::asis_output(out)

```
